---
title: "RosyREDCap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RosyREDCap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load both REDCapSync and RosyREDCap. You can click "Add New Project" in the top left of the shiny app. Alternatively, you can setup projects in R using [REDCapSync](https://github.com/thecodingdocs/REDCapSync "REDCapSync R package"). See the page on [storing tokens](https://thecodingdocs.github.io/REDCapSync/articles/Tokens.html "REDCapSync Tokens"). 

```{r setup,eval=TRUE}
library(REDCapSync)
library(RosyREDCap)
```

Launch the shiny app in your browser with ...

```{r, eval=FALSE}
 # by default will launch in your browser
run_RosyREDCap()
# launch in pop out RStudio window
run_RosyREDCap(options = NULL) 
# launch in RStudio Viewer
run_RosyREDCap(options = c(launch.browser = .rs.invokeShinyPaneViewer)) 
# launch in test_mode (built-in fake projects)
run_RosyREDCap(test_mode = FALSE)
```

You can also use plot functions from the shiny app to make visuals in RStudio.

```{r, eval=TRUE}

TEST_CLASSIC <- load_project("TEST_CLASSIC")
TEST_CLASSIC |> REDCap_diagram()

load_project("TEST_REDCAPR_LONGITUDINAL") |> 
  REDCap_diagram(duplicate_forms = FALSE,
                 hierarchical = TRUE)
```

As more functions are developed they will be shared. Please reach out if you have ideas/suggestions
