---
title: "Security Measures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Security Measures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

RosyREDCap made several design choices to ensure as much security as possible. The owner of the token is ultimately responsible for the path that their data takes. The most important considerations of the user should be the privacy of their token. Regenerate or deactivate if your token has or may have been shared as if your username and password were shared. Never save your token in shared spaces, cloud storage, or in git/github repositories. RosyREDCap cannot control what is done with data once the owner of the token. Ultimately all data coming out of REDCap is recorded in the log.

RosyREDCap encrypts the DB objects that are saved in the user-chosen directory. That file can only be imported into R if that user also has the API token.

```{r setup}
library(RosyREDCap)
```


