---
title: "Tokens"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tokens}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# REDCap API tokens

REDCap API tokens are equivalent to your username and password. They should never be shared with anyone. Ideally, they should never be directly written in an R script, especially if you plan on sharing it in the future. **Never commit a file containing your token on git or GitHub because this will forever be in the history.** If there is ever any doubt in your mind you should quickly regenerate your token on the REDCap website. If you are working on a *real* REDCap project it's good practice to regenerate your token periodically, such as once a week, just to be safe.

Precisely because tokens are sensitive, RosyREDCap is designed to only reference the name of your token, such as "TEST_token". If RosyREDCap ever wants to use the token to make an API call to REDCap, it will check `Sys.getenv("TEST_token")`. Below demonstrates how to set and check your tokens...

## Setting Your Token for One Session

```{r, eval=FALSE}
library("RosyREDCap")
Sys.getenv("TEST_token")
#>[1] ""
```

Unless you specifically set the token `Sys.getenv("TEST_token")` will be blank.

```{r, eval=FALSE}
# Set your token
Sys.setenv(TEST_token="a_FaKe_TOkEn")

# Get your token
Sys.getenv("TEST_token")
#>[1] "a_FaKe_TOkEn"
```

Now the token is set for this R session only. If you restarted R, it would be blank again.

## Setting Your Token for Any Session

You may find want to reuse a token, and you may have several projects, so a convenient way to store the tokens in a separate location. One way to do this is your personal .Renviron file. Again, you should check always confirm the location of this file and make sure it's not a part of any cloud storage or git or GitHub. You can use `usethis::edit_r_environ()` to semi-permanently save your token. Each time you launch an R session this file will run and your token will be visible to you if specifically called with `Sys.getenv("TEST_token")`.

1.  Open the .Renviron file with `usethis::edit_r_environ()`
2.  Add the token like this... `TEST_token = "faKeTokeN"`
3.  Save the file and Close
4.  Restart R Session (Session tab or `.rs.restartR()`).
5.  Confirm with `Sys.getenv("TEST_token")`

```{r, eval=FALSE}
#Install usethis if you don't have it.
#install.packages("usethis") 
usethis::edit_r_environ()
# Now save your token.... (without the comment symbol '#')
# TEST_token = "faKeTokeN"
# Save the file and Close
# Restart R Session (session tab)
# .rs.restartR() # this will also restart R session for you.
Sys.getenv("TEST_token") # now should contain your token
```

The only reference to your token that is ever made or saved in RosyREDCap is with its name. For example, any RosyREDCap DB object will have the token name at `DB$token_name`. In the future, we may set our token in a different way. 

## Testing Your Token (optional)

If you are ever having any issues with your token, you can test your DB object with `view_REDCap_token(DB)` and/or `test_REDCap_token(DB)`

```{r, eval=FALSE}

view_REDCap_token(DB)

test_REDCap_token(DB)

```

## Additional Resources

-   <https://www.dartistics.com/renviron.html>
